Local Spectral Clustering of Density Upper Level Sets

### 2019-06-17 neurips/local_spectral_density_clustering_arxiv.tex
re-org of Theorem 3

\paragraph{Related work.} In addition to the background on local spectral
clustering given previously, a few related lines of work are worth
highlighting. \citep{shi2009,schiebinger2015} examine the consistency of  
spectral algorithms in recovering the latent labels in certain
nonparametric mixture models. Their results focus on global rather than local 
methods, and thus impose global rather than local conditions on the nature
of the density. Moreover, they do not in general guarantee recovery of density 
clusters, which is the focus in our work. Perhaps most importantly, these works
rely on general cluster saliency conditions, which implicitly depend on many
distinct geometric aspects of the cluster $\Cset$ under consideration. We make
this dependence more explicit, and in doing so expose the role each geometric
condition plays in the clustering problem.

>>>>

\paragraph{Related work.} In addition to the background on local spectral
clustering given previously, a few related lines of work are worth
highlighting. \citet{shi2009} and \citet{schiebinger2015} examine the consistency of  
spectral algorithms in recovering the latent labels in certain
nonparametric mixture models. Their results focus on global rather than local 
methods, and thus impose global rather than local conditions on the nature
of the density. Moreover, they do not in general guarantee recovery of density 
clusters, which is the focus in our work. Perhaps most importantly, these works
rely on general cluster saliency conditions, which implicitly depend on many
distinct geometric aspects of the cluster $\Cset$ under consideration. We make
this dependence more explicit, and in doing so expose the role each geometric
condition plays in the clustering problem.
